Automated Verification Applied to Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-07-08 Tex/Old text/abstract.tex
thesis updated text

\thispagestyle{plain}
\begin{center}
    \Large
    \textbf{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}

    \vspace{0.4cm}
    \large
    Optimal Sizing and Project Validation

    \vspace{0.4cm}
    \textbf{Alessandro Trindade}

    \vspace{0.9cm}
    \textbf{Abstract}
\end{center}
verif:
With declining costs and increasing performance, the deployment of renewable energy systems is growing faster. In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends on energy access likewise fall short of global goals. Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible. Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design space. Automated verification using model checking has proven to be an effective technique to validate any kind of system. This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load. Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, were used to evaluate this proposed approach and to compare that with specialized simulation tools. Different verification tools were evaluated as well, in order to compare performance and soundness. Data from practical applications show the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.

synthesis:
There exist various methods and tools to size solar photovoltaic systems; however, the tools are mainly based on simulations, which do not cover all aspects of the design-space. We present a sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis. In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound via symbolic model checking. If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase. Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing. Our synthesis method is novel and unprecedented to streamline the design of PV systems. Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal PV system sizing, and a comparative with a specialized simulation tool and real PV systems shows the effectiveness of our approach.

>>>>

\thispagestyle{plain}
\begin{center}
%    \Large
%    \textbf{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}
%    
%    \vspace{0.4cm}
%    \large
%    Optimal Sizing and Project Validation
%    
%    \vspace{0.4cm}
%    \textbf{Alessandro Trindade}
%    
    \vspace{0.9cm}
    \textbf{Abstract}
\end{center}
With declining costs and increasing performance, the deployment of renewable energy systems is growing faster. In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends on energy access likewise fall short of global goals. Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible. Tools to evaluate or to size electrification projects are available, but they are based on simulations that do not cover all aspects of the design-space. In the other hand, the use of formal methods to model and validate any kind the systems is growing with time, mainly to find bugs in complex hardware and software systems: their aim is to establish system correctness with mathematical rigor. The use of formal methods in electrical systems is a recent subject, with research being published only in the last four years. Moreover, the use of automated synthesis in order to obtain optimal sizing of solar photovoltaic systems was never done before. This Thesis marks two mains achievements: (1) the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load; and (2) a sound and automated approach to obtain optimal sizing of stand-alone photovoltaic systems using program synthesis, where every component and function of a solar photovoltaic system is described, including its properties, and the behavioral model that represents the optimal sizing can be synthesized automatically. Related to formal verification, case studies, from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, were used to evaluate this proposed approach and to compare that with specialized simulation tools. Different verification tools were evaluated as well, in order to compare performance and soundness. Data from practical applications show the effectiveness of the proposed approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method. Moreover, related to the use of program synthesis, it is proposed a variant of counterexample guided inductive synthesis (CEGIS) approach, with two well-defined phases: first it synthesizes the sizing of stand-alone photovoltaic systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound via symbolic model checking. If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase. Commercial equipment data from different manufacturers are provided to the synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing. The proposed synthesis method is novel and unprecedented to streamline the design of photovoltaic systems. Experimental results using seven case studies show that the proposed synthesis method is able to produce within an acceptable run-time the optimal PV system sizing, and a comparative with a specialized simulation tool and real PV systems shows the effectiveness of approach.

### 2019-07-08 Tex/Old text/resumo.tex
thesis updated text

\thispagestyle{plain}
\begin{center}
%    \Large
%    \textbf{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}
%    
%    \vspace{0.4cm}
%    \large
%    Optimal Sizing and Project Validation
%    
%    \vspace{0.4cm}
%    \textbf{Alessandro Trindade}
%    
    \vspace{0.9cm}
    \textbf{Ficha Catalográfica}
\end{center}
\thispagestyle{plain}
Ficha catalog aqui

>>>>

\thispagestyle{plain}
\begin{center}
%    \Large
%    \textbf{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}
%    
%    \vspace{0.4cm}
%    \large
%    Optimal Sizing and Project Validation
%    
%    \vspace{0.4cm}
%    \textbf{Alessandro Trindade}
%    
    \vspace{0.9cm}
    \textbf{Resumo}
\end{center}
Com custos decrescentes e com melhoria de desempenho, a implantação de sistemas de energia renovável está crescendo cada vez mais rapidamente no mundo. Em 2017, pela primeira vez, o número de pessoas sem acesso à eletricidade ficou abaixo de 1 bilhão, mas os dados quanto a universalização do acesso a energia ficaram aquém das metas globais. Particular atenção é dada aos sistemas isolados solares fotovoltaicos em áreas rurais ou onde a extensão da rede é inviável. 
Ferramentas para avaliar ou dimensionar projetos de eletrificação estão disponíveis, mas elas são baseadas em simulações que não cobrem todos os aspectos do espaço de projeto. Por outro lado, o uso de métodos formais para modelar e validar qualquer tipo de sistema está crescendo com o tempo, principalmente para encontrar bugs em sistemas complexos de \textit{hardware} e \textit{software}: seu objetivo é estabelecer a corretude do sistema com rigor matemático. 
O uso de métodos formais em sistemas elétricos é um assunto recente, com pesquisas sendo publicadas apenas nos últimos quatro anos. Além disso, o uso de síntese automatizada para obter um ótimo dimensionamento de sistemas solares fotovoltaicos nunca foi feito antes. 
Esta tese marca duas conquistas principais: (1) a primeira aplicação de modelagem de software para verificar o projeto de um sistema isolado solar fotovoltaico, incluindo painel solar, controlador de carga, bateria, inversor e carga elétrica; e (2) uma abordagem confiável e automatizada para obter o dimensionamento ótimo de sistemas fotovoltaicos usando a síntese de programas, onde cada componente e função de um sistema solar fotovoltaico é descrito, incluindo suas propriedades, e o modelo comportamental que representa o dimensionamento ótimo é sintetizado automaticamente. 
Relacionado a verificação formal, estudos de caso de sistemas fotovoltaicos reais instalados em cinco localidades diferentes foram usados para avaliar a abordagem proposta e para compará-la com ferramenta de simulação especializada.
Diferentes ferramentas de verificação são avaliadas também, a fim de comparar o desempenho e a confiabilidade dos resultados. Dados de aplicações práticas mostram a eficácia da abordagem proposta, onde condições específicas que levam a falhas em um sistema solar fotovoltaico são detalhadas apenas pelo método de verificação automatizado. 
Além disso, em relação ao uso da síntese de programas, propõe-se a variante do método de síntese indutiva guiada por contraexemplos (CEGIS), com duas fases bem definidas: primeiro ele sintetiza o dimensionamento de sistemas fotovoltaicos baseados em confiabilidade de energia, mas que pode não alcançar o menor custo; segundo, a solução proposta é então verificada iterativamente com um limite inferior via verificação de modelo simbólico. Se a etapa de verificação não falhar, o limite inferior será ajustado; e se falhar, o contraexemplo é fornecido com o dimensionamento ótimo, vinculando assim a resposta técnica da primeira fase à análise de custo da segunda fase. Os dados de equipamentos comerciais de diferentes fabricantes são fornecidos ao mecanismo de síntese e as soluções candidatas são derivadas da análise financeira do dimensionamento obtido. O método de síntese proposto é novo e sem precedentes para simplificar o projeto de sistemas fotovoltaicos. Resultados experimentais usando sete estudos de caso mostram que o método de síntese é capaz de produzir em um tempo de execução aceitável o dimensionamento ótimo do sistema fotovoltaico, e um comparativo com uma ferramenta de simulação especializada e sistemas fotovoltaicos reais mostra a eficácia da abordagem adotada.

\textit{Palavras-chave}: Verificação formal; verificação automatizada; verificação de modelos; síntese de programa; sistemas elétricos; sistema solar fotovoltaico
